---
title: "Homework 10"
author: "Shreyasi Tamhane"
date: "2024-04-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results = 'hide', echo = FALSE, warning=FALSE, message=FALSE}
# import libraries
library(ggplot2)
library(tidyverse)
library(mosaic)
library(moderndive)
library(effectsize)
# import datasets
redline <- read.csv("redlining.csv")
groceries <- read.csv("groceries.csv")
```

### Problem 1: Redlining

**Question:** Is there an association between the number of FAIR policies and the racial/ethic composition of a ZIP code.

**Approach:** We will be using a linear regression model to asses whether there is an association between the number of FAIR policies and the racial/ethic composition of a ZIP code.

```{r, echo=FALSE, results = 'hide', warning=FALSE, message=FALSE}
lm_redline = lm(policies ~ minority + fire + age + income, data=redline)
coef(lm_redline) %>% round(4)

confint(lm_redline) %>% round(4)
```

**Results:** The 95% confidence interval of both the age (-0.0020, 0.0132) and income (-0.0935, 0.0616) variables included zero, meaning that these two variables are not statistically significant when considering our question. However, the fire (0.0039, 0.0396) and minority (0.0025, 0.0142) variables did not contain zero, making them statistically significant at the 0.05 level. The minority, fire, and age variables had positive coefficients, 0.0084, 0.0217, 0.0056, respectively. The income variable had a negative coefficient, -0.0160. For every one unit increase of polices given, the percentage of people who identify as a minority in that ZIP code increases by 0.0084. For every one unit increase of polices given, the fires per 100 housing units in that ZIP code increases by 0.0217. For every one unit increase of polices given, the percent of housing units in that ZIP code built before WWII increases by 0.0056. For every one unit increase of polices given, the median family income in thousands of dollars in that ZIP code decreases by -0.0160.

**Conclusion:** Since the 95% confidence interval of both the age and income variables includes zero, it means that they are not statistically significant. Therefore, they seem to not really play a large role in the association between the number of FAIR policies and the racial/ethic composition of a ZIP code. On the other hand, both the fire and minority variables do not contain zero in their 95% confidence intervals, and are thus, statistically significant. Since the coefficients of both the fire and minority variables are positive, it implies that as the number of FAIR policies given increases, the fires per 100 housing units in a ZIP code and the percentage of people who identify as a minority in a ZIP code also increases. Based on this evidence, one could conclude that there is an association between the number of FAIR policies and the racial/ethic composition of a ZIP code.

### Problem 2: Grocery store prices

#### Part A

```{r, echo=FALSE}
groceries_avg_price <- groceries %>% 
  group_by(Store) %>% 
  summarize(avg_price = mean(Price))

ggplot(groceries_avg_price) + 
  geom_col(aes(x=factor(Store), y=avg_price)) +
  coord_flip()
```

The bar graph above shows the average price of the products sold at each of the stores.

#### Part B

```{r, echo=FALSE}
stores_product <- groceries %>% 
  group_by(Product) %>% 
  summarize(num_stores_selling = n_distinct(Store, City))

ggplot(stores_product) + 
  geom_col(aes(x=factor(Product), y=num_stores_selling)) +
  coord_flip()
```

The bar graph above shows the number of stores selling each specific product.

#### Part C

```{r, echo=FALSE, results = 'hide'}
groceries$Type <- factor(groceries$Type)
groceries$Type <- relevel(groceries$Type, ref = "Grocery")
lm_groceries_type = lm(Price ~ Product + Type, data=groceries)

lm_groceries_type_reg_table <- get_regression_table(lm_groceries_type, conf.level = 0.95)
```

Compared with ordinary grocery stores (like Albertsons, HEB, or Krogers), convenience stores charge somewhere between 0.413 and 0.915 dollars more for the same product."

#### Part D

```{r, echo=FALSE, results = 'hide'}
lm_groceries_store = lm(Price ~ Product + Store, data=groceries)
lm_groceries_store_reg_table <- get_regression_table(lm_groceries_store, conf.level = 0.95)
```

The two stores that seem to charge the lowest prices when comparing the same product, are Walmart and Kroger Fresh Fare, with coefficients of -0.993 and -0.902, respectively. The two stores that seem to charge the highest prices when comparing the same product are Whole Foods and Wheatsville Food Co-Op, with coefficients of 364 and 0.290, respectively.

#### Part E

Central Market charges a similar amount to H-E-B for the same product, as their coefficients, -0.573 and -0.646 respectively, do not have that great of a difference, even though Central Market charges slightly higher than H-E-B. The difference between Central Market and H-E-B around 0.073, which is very small. Additionally, this difference is small compared to differences among other stores, such as Wheatsville Food Co-Op, which has a coefficient of 0.290 and Walmart, which has a coefficient of -0.993.

#### Part F

```{r, echo=FALSE, results = 'hide'}
mutated_income <- groceries %>% 
  mutate(Income10K = floor(Income / 10000) + 1)

lm_income = lm(Price ~ Product + Income10K, data=mutated_income)
get_regression_table(lm_income)

standardize_parameters(lm_income)
```

Since the coefficient of the Income10K variable is -0.013, and is negative, it shows that the income decreases as the price of the product increases. As the income in a particular ZIP code increases by \$10,000, the average price paid for the same product decrease by approximately \$0.01. Due to this, it seems that consumers in poorer ZIP codes seem to pay more for the same product, on average.

A one-standard deviation increase in the income of a ZIP code seems to be associated with a -0.03 standard-deviation change in the price that consumers in that ZIP code expect to pay for the same product.
